---
title: "Exercises"
author: "Fatmah"
date: "11/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(recipes)   # for feature engineering
library(tidyverse) # general data munging

# Modeling packages
library(glmnet)   # for implementing regularized regression
library(caret)    # for automating the tuning process
library(rsample)  # for sampling

# Model interpretability packages
library(vip)      # for variable importance
```
#### Using the Hitters dataset from the ISLR package (data(Hitters, package = "ISLR")):

```{r}
library(ISLR)
data(Hitters)

Hitters <- na.omit(Hitters)

set.seed(123)
split <- initial_split(Hitters, strata = "Salary")
Hitters_train <- training(split)

# Create training feature matrices
# we use model.matrix(...)[, -1] to discard the intercept
X <- model.matrix(Salary ~ ., Hitters_train)[, -1]

# transform y with log transformation
Y <- log(Hitters_train$Salary)
```


**1.Apply a ridge model with glmnet with Salary being the response variable.**
- What is the minimum MSE?
- What is the minimum MSE within 1 standard error?
- What are the lambda values for these MSEs?
```{r}
# glment can auto-generate the appropriate lambda values based on the data; the vast majority of the time you will have little need to adjust this default.
ridge <- glmnet(
  x = X,
  y = Y,
  alpha = 0 #0= ridge
)
# plot model coefficients vs. shrinkage parameter lambda
plot(ridge, xvar = "lambda")
```


- What is the minimum MSE(Mean-Squared Error)? 
```{r}
ridge <- cv.glmnet(
  x = X,
  y = Y,
  alpha = 0
)
plot(ridge)

#Ridge model - lambda for this min MSE
min(ridge$cvm)
```

- What is the minimum MSE within 1 standard error?
```{r}
#the largest value of λ such that the error is within 1 standard error of the minimum
ridge$cvm[ridge$lambda == ridge$lambda.1se]

```
- What are the lambda values for these MSEs?
```{r}
# Ridge model w/1-SE rule -- No. of coef | 1-SE MSE
ridge$nzero[ridge$lambda == ridge$lambda.1se]
```

**2.Apply a lasso model with glmnet.**
- What is the minimum MSE?
- What is the minimum MSE within 1 standard error?
- What are the lambda values for these MSEs?

```{r}
#Apply a lasso model with glmnet.
lasso <- glmnet(
  x = X,
  y = Y,
  alpha = 1 #1= lasso
)

plot(lasso, xvar = "lambda") #xvar = testing for all version of lambda
```

- What is the minimum MSE?
```{r}
lasso <- cv.glmnet(
  x = X,
  y = Y,
  alpha = 1
)

plot(lasso)

#What is the minimum MSE?
min(lasso$cvm)
```

- What is the minimum MSE within 1 standard error?
```{r}

# Lasso model - w/1-SE rule
lasso$cvm[lasso$lambda == lasso$lambda.1se]
```

- What are the lambda values for these MSEs?
```{r}
# Lasso model w/1-SE rule -- No. of coef | 1-SE MSE
lasso$nzero[lasso$lambda == lasso$lambda.1se]
```

**3.Perform a grid search across alpha parameter values ranging between 0–1.**
####Grid search
Often, the optimal model contains an alpha somewhere between 0–1, thus we want to tune both the λ and the alpha parameters. 
```{r}
#Perform a grid search across alpha parameter values ranging between 0–1.
hyper_grid <- expand.grid( # The hyper_grid will have all the compination between alpha and lambda values
  alpha = seq(0, 1, by = .25),
  lambda = c(0.1, 10, 100, 1000, 10000)
)

# perform resampling
set.seed(123)
cv_glmnet <- train(
  x = X,
  y = Y,
  method = "glmnet", # we use the meta engen
  preProc = c("zv", "center", "scale"), #zv = remove the zero variance
  trControl = trainControl(method = "cv", number = 10),
  tuneLength = 10
)
```

#What is the optimal alpha and lambda values?
```{r}
# best model
cv_glmnet$results %>%
  filter(
    alpha == cv_glmnet$bestTune$alpha, #optimal alpha
    lambda == cv_glmnet$bestTune$lambda #optimal lambda
    )
```


#What is the MSE and RMSE for this optimal model?
```{r}

```


#How does it compare to your previous models?
```{r}
# predict salary on training data
pred <- predict(cv_glmnet, X)
# compute RMSE of transformed predicted
RMSE(exp(pred), exp(Y))
```

**4.Plot the top 10 most influential features. Do these features have positive or negative impacts on your response variable?**
```{r}
plot(cv_glmnet)
```

